Statistical Machine Learning Models on A Bank Marketing Dataset

### 2025-12-09 Slides.Rmd
slides update6

---
title: "Statistical Machine Learning Models on A Bank Marketing dataset"
author: "Sandra, Tigist, Mussa Hassen, Waddah"
subtitle: 'Colorado State University, DSCI 445: Statistical Machine Learning, Dr.Andee
  Kaplan'
output:
  ioslides_presentation:
    widescreen: true
---

@@

```{r slide2-plot, echo=FALSE, fig.align="center", out.width="90%"}
knitr::include_graphics("EDA/imbalance_plot.png")
```

@@

```{r eda1-plot, echo=FALSE, fig.align="center", out.width="90%"}
knitr::include_graphics("EDA/contact_plot.png")

@@

```{r eda2-plot, echo=FALSE, fig.align="center", out.width="90%"}
knitr::include_graphics("EDA/poutcome_plot.png")
```

@@

```{r eda3-plot, echo=FALSE, fig.align="center", out.width="90%"}
knitr::include_graphics("EDA/campaign_plot.png")
```

## Problem Statement & Methodology Overview

* **Goal:** Compare models on two criteria:  
  * **Predictive Power** – ability to correctly find YES cases  
  * **Interpretability** – model is easy to understand

* **Model evaluation:**  
  * **80/20 Train/Test Split**  
  * **5-Fold Cross-Validation**

@@

## Business Impact
* The central trade-off: Boosting is the best predictor, but the **Regularized Logistic Regression** offers the most *interpretable* and *actionable* insights for the bank.
* Sample coefficients: $\beta_{Balance^2}$ = -23.02, $\beta_{Housing}$ = -0.65, $\beta_{JobStudent}$ = 4.064
* The chosen model can lead to cost savings and higher ROI for future campaigns.
* **Image/Plot Idea:** A visual metaphor (e.g., a scale or seesaw) contrasting "High Performance" vs. "High Interpretability."

>>>>

---
title: "Statistical Machine Learning Models on A Bank Marketing Dataset"
author: "Sandra, Tigist, Mussa Hassen, Waddah"
subtitle: 'Colorado State University, DSCI 445: Statistical Machine Learning, Dr.Andee
  Kaplan'
output:
  ioslides_presentation:
    widescreen: true
---

@@

```{r slide2-plot, echo=FALSE, fig.align="center", out.width="75%"}
knitr::include_graphics("EDA/imbalance_plot.png")
```

@@

```{r eda1-plot, echo=FALSE, fig.align="center", out.width="75%"}
knitr::include_graphics("EDA/contact_plot.png")
```

@@

```{r eda2-plot, echo=FALSE, fig.align="center", out.width="68%"}
knitr::include_graphics("EDA/poutcome_plot.png")
```

@@

```{r eda3-plot, echo=FALSE, fig.align="center", out.width="75%"}
knitr::include_graphics("EDA/campaign_plot.png")
```

@@

## Business Impact
* The central trade-off: Boosting is the best predictor, but the **Regularized Logistic Regression** offers the most *interpretable* and *actionable* insights for the bank.
* Sample coefficients: $\beta_{Balance^2}$ = -23.02, $\beta_{Housing}$ = -0.65, $\beta_{JobStudent}$ = 4.064
* The chosen model can lead to cost savings and higher ROI for future campaigns.
